\section{Conclusion}
Based on the analysis we came to the conclusion that our target group is hobbyists or home brewers.
We have also concluded that the most important features for our target group is the ability to simplify the brewing process and
make it easier and less time consuming, this is necessary since brewing process is very complex and time consuming
as we do not expect our users to have any prior experience or expertise in brewing.\newline

With the help of the analysis, requirements for the project was made.
Based on these requirements we made a design for the system.
In the design we decided to use a client-server architecture, where the client is a web application and the server is a REST API.
The REST API is used to communicate with the database and the OPC-UA client.
The OPC-UA client is used to communicate with the machine, where the brewing process takes place.
We also made a database for storing the order with the beer type, the amount of beers and the timestamp.\newline

The implementation of the system was made with the design in mind.
In the web application we decided to use a single page application (SPA) with the UI library React,
since it makes it easier to update the UI without having to reload the page.
We decided to go for a backend with Node.js instead of Java, because it is easier to use and faster to develop with than Java.
The Milo OPC-UA library in Java is running on Java 8, which is a very old version.
The REST API was made with the framework Express and the OPC-UA client was made with the library node-opcua.
The database was made with the database PostgreSQL, using the pg library.\newline

To make sure our system worked as we intended, we tested the system.
We made unit tests for the Express REST API backend and for the OPC-UA client.
We also tested each of the beer types with different speeds and observed the fail rate,
as one of our requirements was to aim for optimal speed for each beer type.
From the data gathered, graphs were made for each beer type together with a regression line.
Based on that regression line we solved for having a failrate of 1\%.
As negative speeds are not possible we decided to use 1 as the speed for Ale and Alcohol Free.\newline

Overall, we have made a simplified and automated system for hobbyists and home brewers,
that has been tested and optimized. The system uses the client-server architecture with a Node.js REST API backend,
using an OPC-UA client, which is connected to the OPC-UA server, and React frontend together with storing the orders in a PostgreSQL database.